### 2018-06-11 VV570/HW3/assignment.tex
add ex4

%----------------------------------------------------------------------------------------
%	PROBLEM 2
%----------------------------------------------------------------------------------------
\section{Cantor's Function}
	\begin{enumerate}
		\item
			\begin{proof}
				It's easy to verify that $f_0, f_1$ are monotonically increasing continuous functions.\\
				Suppose $f_n$ are still monotonically increasing continuous functions for $ n = k$.\\
				For $n = k+1$, as $f_{k+1}$ is only different from $f_k$ on each closed subset of $C_k$, whose length is $\frac{1}{3^n}$ and is denoted as $I_{k, p} (1\leq p \leq 2^k$) here, it is left to prove that $f_{k+1}$ remains  monotonically increasing continuous on each $I_{k, p}$ after the construction process.\\
				Since $f_k$ is linear on each $I_{k, p}$, and the recursive construction process doesn't change the values on each ending points, on which the values of $f_k$ is denoted as $a, b$ recursively, the subset of $I_{k, p}$ is valid and the value of $f_{k+1}$ on the central part, whose length is $\frac{1}{3^{k+1}}$, is $\frac{a+b}{2}$. As the measure of the remaining parts of $I_{k, p}$ is not 0, the linear function connecting each ending points is obviously valid. Thus, the new function $f_{k+1}$ is still  monotonically increasing continuous.
			\end{proof}
		\item
			\begin{proof}
				Let $g_n(x) = \vert f_n(x) - f(x) \vert$, then $g_n(x)$ is positive on $C_n$ and 0 on other places. Further, $g_n(x)$ is symmetric around $x = 1/2$, thus, only $[0, 1/2]$ is considered for simplicity.\\
				Given any $\xi > 0$, it is left to find $N$ s.t. $g_n(x) < \xi$ when $n > N$.
			\end{proof}
		\item

@@

%----------------------------------------------------------------------------------------
%	PROBLEM 4
%----------------------------------------------------------------------------------------
\section{Convergence of rationals to irrationals}
	\begin{enumerate}
		\item

>>>>

%----------------------------------------------------------------------------------------
%	PROBLEM 2
%----------------------------------------------------------------------------------------
\section{Cantor's Function}
	\begin{enumerate}
		\item
			\begin{proof}
				It's easy to verify that $f_0, f_1$ are monotonically increasing continuous functions.\\
				Suppose $f_n$ are still monotonically increasing continuous functions for $ n = k$.\\
				For $n = k+1$, as $f_{k+1}$ is only different from $f_k$ on each closed subset of $C_k$, whose length is $\frac{1}{3^n}$ and is denoted as $I_{k, p} (1\leq p \leq 2^k$) here, it is left to prove that $f_{k+1}$ remains  monotonically increasing continuous on each $I_{k, p}$ after the construction process.\\
				Since $f_k$ is linear on each $I_{k, p}$, and the recursive construction process doesn't change the values on each ending points, on which the values of $f_k$ is denoted as $a, b$ recursively, the subset of $I_{k, p}$ is valid and the value of $f_{k+1}$ on the central part, whose length is $\frac{1}{3^{k+1}}$, is $\frac{a+b}{2}$. As the measure of the remaining parts of $I_{k, p}$ is not 0, the linear function connecting each ending points is obviously valid. Thus, the new function $f_{k+1}$ is still  monotonically increasing continuous.
			\end{proof}
		\item
			\begin{proof}
				Let $g_n(x) = \vert f_n(x) - f(x) \vert$, then $g_n(x)$ is positive on $C_n$ and 0 on other places. Further, $g_n(x)$ holds the same value on each closed subset of $C_n$.\\
				Given any $\xi > 0$, it is left to find $N$ s.t. $g_n(x) < \xi$ when $n > N$. \\
				As $g_n(x)$ reaches its extream $\frac{1}{6} \frac{1}{3^n}$ at the $\frac{1}{3}$ and $\frac{2}{3}$ of each compact subset of $C_n$, thus, given any $\xi$

				\begin{equation}
					\frac{1}{6} \frac{1}{3^n} < \xi
				\end{equation}

				which is equivalent to

				\begin{equation}
					n > \frac{ln(\frac{1}{6\xi})}{ln(3)} \triangleq N
				\end{equation}

				and the target $N$ is given as above.
			\end{proof}
		\item 
			\begin{proof}
				As $f_c(x)$ is continous over $[0, 1]$, it is left to prove that a continous function on a compact is uniformly continous, which can be proved by contradiction.

			\end{proof}

@@

%----------------------------------------------------------------------------------------
%	PROBLEM 4
%----------------------------------------------------------------------------------------
\section{Convergence of rationals to irrationals}
	\begin{enumerate}
		\item
			\begin{proof}
				As $e$ can be written as 
				\begin{equation}
					e = \sum_{i=0}^{\infty} \frac{1}{i!}
				\end{equation}

				Suppose it is rational, then it can be written as below, where $p, q$ are prime to each other.

				\begin{equation}
					e = \frac{p}{q} 
				\end{equation}
				Thus
				\begin{equation}
					p(q-1)! = q! \sum_{i=0}^{q} \frac{1}{i!} +  q! \sum_{i=q+1}^{\infty} \frac{1}{i!} 
				\end{equation}
				Since both LHS  and  the first part of RHS are integers, the second part of RHS(denoted as $RHS_2$) should be an integer as well.//
				$RHS_2$ can be further expanded as below
				\begin{equation}
					\begin{aligned}
						RHS_2 & = \frac{1}{q+1} + \frac{1}{(q+1)(q+2)} + \frac{1}{(q+1)(q+2)(q+3)} + ...\\
						           & <  \frac{1}{q+1} + \frac{1}{(q+1)^2} + \frac{1}{(q+1)^3} + ...\\
						           & = \frac{1}{q}\\
						           & < 1
					\end{aligned}
				\end{equation}
				Therefore $RHS_2$ is not an integer as $RHS_2 > 0$. Thus the assumption fails, and $e$  is irrational.
			\end{proof}

		\item
			\begin{proof}
				It's clear that $u_n$ is increasing, and the limit is $e$, so the maximum distance between 2 element can be denoted as 
				\begin{equation}
					d_{max} < e - (1+\frac{1}{n})^n
				\end{equation}

				For any $\xi > 0$, let $d_{max} < \xi$, it is satisfied when $n > N $, where $N$ is the index of the first element s.t. $u_N > e-\xi$.\\
				Thus $u_n$ is a cauchy sequence converging to $e$.
			\end{proof}

		\item
			No, as the limit of a rational sequence may not converging to a rational.
	\end{enumerate}
